|

### 2021-05-11 paper/v2_taylor_francis_for_proof/broadband.speed.covid_for_tables.Rmd
not my day... the revised .Rmd for the .tex tables

stargazer(clustersLADup[1:7],
          summary = F,
          font.size = "footnotesize",
          type = "latex",
          header = F,
          digit.separator = ",",
          digit.separate = c(3,3),
          covariate.labels=c("Cluster",
                             "N. of LADs",
                             "LAD population",
                             "mean speed",
                             "SD speed",
                             "mean AM speed",
                             "mean PM speed"),
                             #"AM_slower",
                             #"SDtoMean"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt",
          notes = "Note: All speed measures are upload speeds",
          title = "Upload speed cluster characteristics\\label{up.cluster.descr}")
```

@@

stargazer(aux.up,
          type = "latex",
          nobs = T,
          digits = 3,
          font.size = "tiny",
          float.env = "sidewaystable",
          dep.var.caption = "",
          title = "Auxiliary multinomial regression of upload speed clusters on socio-economic and geographic LAD variables\\label{aux}",
          header = F,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "service jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "furloughed per hab., 2020",
                             "AM tests per hab., 2020",
                             "Virgin Media \\%, 2020"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))
```

@@

stargazer(for.descr,
          summary = T,
          font.size = "footnotesize",
          type = "latex",
          header = F,
          digit.separator = ",",
          digit.separate = c(3,3),
          covariate.labels=c("pop, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "south of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "service jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "Virgin Media \\%, 2020",
                             "n. business est. per hab., 2019",
                             "AM tests per hab., 2020",
                             "furloughed per hab., 2020"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt",
          #notes = "",
          title = "Descriptive statistics for the auxiliary regression explanatory variables\\label{descr.aux}")
```

>>>>

path.out = paste0(path, "/paper/v2_taylor_francis_for_proof/tables/table_1.tex")

stargazer(clustersLADup[1:7],
          summary = F,
          type = "latex",
          out = path.out,
          font.size = "footnotesize",
          header = F,
          digit.separator = ",",
          digit.separate = c(3,3),
          covariate.labels=c("Cluster",
                             "N. of LADs",
                             "LAD population",
                             "mean speed",
                             "SD speed",
                             "mean AM speed",
                             "mean PM speed"),
                             #"AM_slower",
                             #"SDtoMean"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt",
          notes = "Note: All speed measures are upload speeds",
          title = "Upload speed cluster characteristics\\label{up.cluster.descr}")
```

@@

path.out = paste0(path, "/paper/v2_taylor_francis_for_proof/tables/table_2.tex")

stargazer(aux.up,
          type = "latex",
          out = path.out,
          nobs = T,
          digits = 3,
          font.size = "tiny",
          float.env = "sidewaystable",
          dep.var.caption = "",
          title = "Auxiliary multinomial regression of upload speed clusters on socio-economic and geographic LAD variables\\label{aux}",
          header = F,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "service jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "furloughed per hab., 2020",
                             "AM tests per hab., 2020",
                             "Virgin Media \\%, 2020"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))
```

@@

path.out = paste0(path, "/paper/v2_taylor_francis_for_proof/tables/table_A1.tex")

stargazer(for.descr,
          summary = T,
          out = path.out,
          font.size = "footnotesize",
          type = "latex",
          header = F,
          digit.separator = ",",
          digit.separate = c(3,3),
          covariate.labels=c("pop, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "south of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "service jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "Virgin Media \\%, 2020",
                             "n. business est. per hab., 2019",
                             "AM tests per hab., 2020",
                             "furloughed per hab., 2020"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt",
          #notes = "",
          title = "Descriptive statistics for the auxiliary regression explanatory variables\\label{descr.aux}")
```
